Structured Versus Decorated Cospans

### 2021-06-28 cospans_new.tex
I put the mistakenly deleted paragraph after Lemma 2.4 back in.

{\chris There was a paragraph here (under (21) in old version) which I think is used in what follows, since that is the version of the theorem we actually use, the cocartesian total category one!}

>>>>

These 2-equivalences further restrict to the case when the Grothendieck category $(X,\otimes_\X)$ is specifically cocartesian monoidal itself, with coproducts built up from \cref{eq:explicitstructure2}. In that case, opfibrations $(\X,+) \to (\A,+)$ that strictly preserve coproducts and initial object bijectively correspond to pseudofunctors into the 2-category of cocartesian categories.  For more details, see \cite[Corollary 4.7]{MV} and the related discussion.
